
\section*{\huge Section 3}

\section{Platforms Used}

In the development of our project, we have chosen to utilize both Visual Studio 2022 \footnote{{\url:https://visualstudio.microsoft.com/vs//}} and GitHub. \footnote{{\url{https://github.com/givenmnisi6/Cryptography-Project}}}

\subsection{Visual Studio 2022} 
For building, editing, and GUI (Graphical User Interfaces), as well as deploying applications, Visual Studio is the ideal platform to use. We utilized the .NET Framework in C\# to develop our application. We used it because of the following reasons (Microsoft, 2023): 

\begin{enumerate}
   \item Cross-platform compatibility: C\# is easy to develop applications in all Operating systems. Which makes it more versatile.
   \item Object-oriented programming: C\# is well suited for creating complex applications which support inheritance, abstract classes, and more
   \item Large community: In C\# there are a lot of resources that can assist you with troubleshooting.
\end{enumerate}

\subsection{GitHub}
In our project, we utilized GitHub throughout every development process. It makes version control easy and collaborates with others easily. We used it because of the following reasons (Kharlantseva, 2023): 


\begin{enumerate}
   \item Version control: makes it easy to track every process and allows for easy rollback to a stable version when changes have been made that break the code
   \item Integration with other apps: GitHub can easily integrate with other IDEs such as Visual Studio 2022 and many more. Making it easy to automate the development process

\end{enumerate}


